Chronic imaging of cortical oxygen tension and blood flow after targeted vascular occlusion

### 2018-04-06 article.tex
Added details to Figure 2 caption
Better describe how shorter lifetimes are handled in computing pO2

% Figure 2 - Oxyphor PtG4
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure2.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:oxyphor_ptg4}
        (a) Excitation and emission spectra for Oxyphor PtG4. Dashed vertical lines indicate excitation lasers at 445 nm and 637 nm. (b) Calibration curve relating \pO\ to the measured phosphorescence lifetime ($\tau$) under physiological conditions (37 $^\circ$C, pH 7.2). (c) Phosphorescent decay curves in anoxic and normoxic environments with fitted lifetimes and their corresponding \pO\ values.
    }
\end{figure}

>>>>

% Figure 2 - Oxyphor PtG4
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure2.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:oxyphor_ptg4}
        (a) Excitation and emission spectra for Oxyphor PtG4. Dashed vertical lines indicate excitation lasers at 445 nm and 637 nm. (b) Calibration curve relating \pO\ to the measured phosphorescence lifetime ($\tau$) under physiological conditions (37 $^\circ$C, pH 7.2). For $\tau < 16$ $\mu$s, Stern-Volmer kinetics were assumed with $k_q = 291.014$ mmHg$^{-1}$ s$^{-1}$ and $\tau_0 = 47$ $\mu$s. (c) Averaged phosphorescent decay curves ($n = 200$) in anoxic and normoxic cuvette environments with fitted lifetimes and their corresponding \pO\ values.
    }
\end{figure}
